### 2022-08-20 data/example.tex
Support linline tags for Latex
Update readme

\newenvironment{lcode}
  {\VerbatimEnvironment
   \begin{mdframed}
   \begin{minted}[breaklines, fontsize=\footnotesize]{python}}
  {\end{minted}
   \end{mdframed}}
\newenvironment{lresult}
  {\begin{mdframed}}
  {\end{mdframed}}

@@

LitREPL for latex recognizes specifically named environments as code and result
sections. It doesn't really evaluate Tex commands so renaming those environments
wouldn't work. But we still need to introduce it to Latex so we start with a
newenvironment declarations.

\begin{verbatim}
\newenvironment{lcode}
  {\VerbatimEnvironment
   \begin{mdframed}
   \begin{minted}[breaklines, fontsize=\footnotesize]{python}}
  {\end{minted}
   \end{mdframed}}
\newenvironment{lresult}
  {\begin{mdframed}[leftline=false,rightline=false]}
  {\end{mdframed}}
\end{verbatim}

@@

Executable code snippet is the content of the \texttt{lcode} environment.
Putting the cursor on it and typing the \texttt{:LitEval1} command runs it
it in a background Python interpreter.

@@

\texttt{lresult} section next to the executable section is a result container.
LitREPL would paste here the output of above code snippet. The original content
of the section will be replaced.

@@

Commented \texttt{lresult} environmet tags are still recognized as a section for
verbatim results. This way users can generate parts of the latex document.

@@

\begin{mdframed}
%\begin{lresult}
Hello LitREPL.vim
%\end{lresult}
\end{mdframed}

\section{Invoking Mathplotlib code}

\begin{lcode}
import numpy as np
import matplotlib.pyplot as plt
X=np.array(range(10))
_=plt.plot(X, np.sin(X))
def texplot(f):
  plt.savefig(f)
  print("\\includegraphics{./"+f+"}")

texplot('_img.png')
\end{lcode}

\newcommand{\linplace}[2]{#2}
%\begin{lresult}
\includegraphics{\linplace{VAR}{_img.png}}
%\end{lresult}

>>>>

\newenvironment{lcode}
  {\VerbatimEnvironment
   \begin{mdframed}
   \begin{minted}[breaklines, fontsize=\footnotesize]{python}}
  {\end{minted}
   \end{mdframed}}
\newenvironment{lresult}
  {\begin{mdframed}}
  {\end{mdframed}}
\newcommand{\linline}[2]{#2}

@@

LitREPL treats specially named Latex environments as code and result sections.
It doesn't really evaluate \TeX\ commands so the tags should present in the source
file explicitly rather than be a result of other commands such as
\texttt{newcommand} or \texttt{newenvironment}.

\begin{verbatim}
\newenvironment{lcode}
  {\VerbatimEnvironment
   \begin{mdframed}
   \begin{minted}[breaklines, fontsize=\footnotesize]{python}}
  {\end{minted}
   \end{mdframed}}
\newenvironment{lresult}
  {\begin{mdframed}[leftline=false,rightline=false]}
  {\end{mdframed}}
\newcommand{\linplace}[2]{#2}
\end{verbatim}

@@

Executable code is obtained from the content of the \texttt{lcode} environment.
Putting the cursor on this environment and typing the \texttt{:LitEval1} Vim
command sends the code to the Python interpreter persistently running in the
background.

\begin{verbatim}
\begin{lcode}
W='Hello, world!'
print(W)
\end{lcode}
\end{verbatim}

@@

\texttt{lresult} section next to the executable section is a result container.
When executed, LitREPL replaces its content with the executable code output.

\begin{verbatim}
\begin{lresult}
??
\end{lresult}
\end{verbatim}

@@

VimREPL also recognises commented \texttt{lresult} tags as a valid result
container. This we can generate custom parts of the document.

@@

\begin{verbatim}
%\begin{lresult}
??
%\end{lresult}
\end{verbatim}

\begin{mdframed}
%\begin{lresult}
Hello, LitREPL.vim!
%\end{lresult}
\end{mdframed}

A special two-argument \texttt{linline} tag works both as an executable section
and as a result container. We expect it to be used to print the contents of
Python variables, so the VimREPL wraps the executable code with the additional
\texttt{print(...)} operator. On the Latex side, we define the tag to ignore its
first argument but pass the second one as-is.

\begin{verbatim}
\begin{mdframed}\linline{W}{??}\end{mdframed}
\end{verbatim}

\begin{mdframed}\linline{W}{Hello, world!}\end{mdframed}

\section{Mathplotlib plots and other graphics}

\begin{lcode}
import numpy as np
import matplotlib.pyplot as plt
X=np.array(range(10))
plt.plot(X, np.sin(X))
path='_img.png'
plt.savefig(path)
\end{lcode}

\includegraphics{\linline{path}{_img.png}}
